00-Data-Processing-for-sobiEquity

### 2021-03-19 sobiEquity/raw-data-processing/00-Data-Processing-for-sobiEquity.Rmd
Revised in hub in data package and worked with figures and tables for style

Identify hubs that were deactivated:
```{r}
sobi_hubs <- sobi_hubs %>%
  dplyr::mutate(hub_status = case_when(OBJECTID == 114 ~ "Deactivated",
                                       OBJECTID == 115 ~ "Deactivated",
                                       OBJECTID == 116 ~ "Deactivated",
                                       TRUE ~ "Active"),
                hub_status = factor(hub_status))

>>>>

Identify hubs that were deactivated:
```{r}
sobi_hubs <- sobi_hubs %>%
  dplyr::mutate(hub_status = case_when(OBJECTID == 115 ~ "Deactivated",
                                       OBJECTID == 116 ~ "Deactivated",
                                       TRUE ~ "Active"),
                hub_status = factor(hub_status))
